### 2023-05-11 proposal-documents/white-paper/white-paper-general-preproposal.tex
reset

%%%%% watermark
%\usepackage[firstpage,vpos=0.63\paperheight]{draftwatermark}
%\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
%\SetWatermarkScale{0.20}
%%%%%

@@

\section*{Workscopes in Brief}
\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=0.5in]
    \item\textbf{X.} (\textit{Lead - ; Support - , })
        \begin{enumerate}[topsep=3pt,itemsep=1ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.25in]
            \item\textit{x.}
            \item\textit{x.}
        \end{enumerate}
    \item\textbf{X.} (\textit{Lead - ; Support - , })
        \begin{enumerate}[resume,topsep=3pt,itemsep=1ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.25in]
            \item\textit{x.}
            \item\textit{x.}
        \end{enumerate}
\end{enumerate}

\section*{Importance and Relevance to Objectives} 
\subsection*{Background}

\subsection*{Relevant literature}

\subsection*{Recently funded work}

\subsection*{Unique project features}

\section*{Research Workscopes \& Tasks}

\section*{Logical path to work accomplishment} 
\begin{enumerate}[series=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{Workscope title} 
        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{This task.}
            \item\textit{That task.}
            \item\textit{Another task.}
                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item A brief explanation or a subtask if needed.
                \end{enumerate*}
        \end{enumerate}
\end{enumerate}

@@

\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{Workscope title} 
        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{This task.}
            \item\textit{That task.}
            \item\textit{Another task.}
                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item A brief explanation or a subtask if needed.
                \end{enumerate*}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{Workscope title} 
        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{This task.}
            \item\textit{That task.}
            \item\textit{Another task.}
                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item A brief explanation or a subtask if needed.
                \end{enumerate*}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{Workscope title} 
        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{This task.}
            \item\textit{That task.}
            \item\textit{Another task.}
                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item A brief explanation or a subtask if needed.
                \end{enumerate*}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{Crosscutting discussions \& follow on activities.} 
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{Identify lessons learned.}
                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Lessons learned will be applied to \ldots . 
                \end{enumerate*}
            \item\textit{Develop future work.}
                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item \ldots.
                    \item \ldots.
                    \item \ldots.
                \end{enumerate*}
            \item\textit{Reproducibility \& validation.}
                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Explore avenues to reproduce and validate results \ldots .
                \end{enumerate*}
        \end{enumerate}
\end{enumerate}

@@

\begin{longtable}{|L{0.23\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
%       \captionsetup{margin=-0pt}
        \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
        \label{tab-timeline}\\
        \hline
        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}& 
        \multicolumn{4}{|c|}{\textbf{Y1}}&
        \multicolumn{4}{|c|}{\textbf{Y2}}&
        \multicolumn{4}{|c|}{\textbf{Y3}}
        \\
        \cline{2-13}
        &
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}
        \\
        \hline
        I. 
        &\x\textbf{X}
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        II. 
        &\x\textbf{X} 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        III. 
        &\x\textbf{X} 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        IV. 
        &\x\textbf{X}
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        V. 
        &\x\textbf{X} 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        VI. 
        &\x\textbf{X} 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        XI. Lessons learned
        &
        &
        &
        &
        &\x
        &\x
        &\x
        &\x
        &\x
        &\x
        &
        &
        \\
        \hline
        XII. Future work
        &
        &
        &
        &
        &
        &
        &
        &
        &\x
        &\x
        &\x
        &
        \\
        \hline
        XIII. Reprod. \& validation
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &\x
        &\x
        \\
        \hline
\end{longtable}

\part*{References}
\bibliographystyle{nsf}
\setlength{\bibhang}{0pt}
\bibliography{references}

@@

%\section{Title}\label{app-}

@@

%wrap figure around text
%move to wherever in the text 
%{l} fixes it on the left margin
%{L} floats
%\begin{wrapfigure}{l}{0.x\textwidth}
%       \includegraphics[width=0.(x-2)\textwidth]{}
%    \caption{}
%    \label{fig-}
%\end{wrapfigure}

>>>>

%%%%% watermark
\usepackage[firstpage,vpos=0.63\paperheight]{draftwatermark}
\SetWatermarkText{\shortstack{CONFIDENTIAL\\do not distribute}}
\SetWatermarkScale{0.20}
%%%%%

@@

\section*{Workscopes in Brief}
\begin{enumerate}[series=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - , })
        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
            \item\textit{.}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
            \item\textit{.}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
            \item\textit{.}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
            \item\textit{.}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{Crosscutting discussions \& follow on activities.} (\textit{Full team})
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{Identify lessons learned.}
            \item\textit{Develop future work.}
            \item\textit{Reproducibility \& validation.}
        \end{enumerate}
\end{enumerate}

\section*{Relevant Background}

\section*{Related Research \& Funding Efforts}

\section*{Team synergy}

\section*{Unique project features}

\section*{Logical path to work accomplishment} 
\begin{enumerate}[series=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{Workscope title} (\textit{Lead - ; Support - })
        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{This task.}
            \item\textit{That task.}
            \item\textit{Another task.}
                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item A brief explanation or a subtask if needed.
                \end{enumerate*}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

@@

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{Workscope title} (\textit{Lead - ; Support - })
        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{This task.}
            \item\textit{That task.}
            \item\textit{Another task.}
                \begin{enumerate*}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item A brief explanation or a subtask if needed.
                \end{enumerate*}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will \ldots}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will \ldots}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume=outerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will \ldots}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will \ldots}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will \ldots}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{Crosscutting.} (\textit{Lead - ; Support - Full team})
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{Identify lessons learned.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{Develop future work.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{Reproducibility \& validation.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will wrapup the major findings of project activities and pursue new avenues of research with colleagues in the field.}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

@@

\begin{longtable}{|L{0.23\linewidth}|c|c|c|c|c|c|c|c|c|c|c|c|}
%       \captionsetup{margin=-0pt}
        \caption*{\textbf{Timeframe for Execution of Proposed Project. Schedule, Roles, and Responsibilities.}}
        \label{tab-timeline}\\
        \hline
        \multicolumn{1}{|c|}{\multirow{2}{*}{\textbf{TASKS}}}& 
        \multicolumn{4}{|c|}{\textbf{Y1}}&
        \multicolumn{4}{|c|}{\textbf{Y2}}&
        \multicolumn{4}{|c|}{\textbf{Y3}}
        \\
        \cline{2-13}
        &
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}& 
        \textbf{Q1}& 
        \textbf{Q2}& 
        \textbf{Q3}& 
        \textbf{Q4}
        \\
        \hline
        I. 
        &\x
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        II. 
        &\x
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        III. 
        &\x 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        IV. 
        &\x
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        V. 
        &\x 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        VI. 
        &\x 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        & 
        \\
        \hline
        XI. Lessons learned
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &\x
        &\x
        \\
        \hline
        XII. Future work
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &\x
        &\x
        \\
        \hline
        XIII. Reprod. \& validation
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &
        &\x
        &\x
        \\
        \hline
\end{longtable}

@@

%    \section{Acronyms}
%    \printnoidxglossary[title={}]

%    \section{Title}\label{app-}

@@

%remove page break if there are page limits
%\vspace{0.5\baselineskip}

\part*{References}
\bibliographystyle{nsf}
%\bibliographystyle{neup}
\setlength{\bibhang}{0pt}
\bibliography{references}

%%%%%%% wrap figure around text
%move to wherever in the text
%{l} fixes it on the left margin
%\begin{wrapfigure}{l}{0.x\textwidth}
%        \includegraphics[width=0.(x-2)\textwidth]{filename.ext}
%    \caption{}
%    \label{fig-}
%\end{wrapfigure}
%%%%%%%
